The K2 Bright Star Survey

### 2019-05-16 paper/ms.tex
owl reference

% describe halo algorithm
This method was first described by \citet{White2017} and applied to the Pleiades' Seven Sisters, and was applied to Aldebaran with further developments by \citet{Farr2018}. Because SAP is not possible, we consider instead the unsaturated pixels $p_j$ at the wings of the broad and structured PSF. We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux at cadence $i$ is

@@

%  improvements
Unlike other methods for calibrating \kepler systematics, other than the value of $\delta$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm. The method is a self-calibration that is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise. It is therefore likely that significant improvements can be made to the method by including cotrending basis vectors with mean zero and whose weights are allowed to be negative, which would represent systematics which are common to all pixels in the halo aperture and therefore masquerade as signal. Any linear combination of convex objective functions is itself convex, and future extensions to the method could enforce combinations of different lags and orders to better represent systematics occurring on different timescales (e.g. thruster firings, red noise) and with different levels of smoothness.

>>>>

% describe halo algorithm
This method was first described by \citet{White2017} and applied to the Pleiades' Seven Sisters, and was applied to Aldebaran with further developments by \citet{Farr2018}. We follow the `OWL' concept described by Hogg \&  Foreman-Mackey (2014, unpublished: preprint  \href{https://github.com/davidwhogg/OWL/}{\nolinkurl{github.com/davidwhogg/OWL/}}) in our assumptions. We assume that a star has a wide PSF sampled by many pixels with different sensitivities, which moves around on the detector within a small region and which may vary to a small extent in time. We do not have metadata describing the spacecraft motion, pixel gains, PSF variations or noise processes. Because photometry is a linear operation, any estimator of the flux is necessarily a weighted sum of pixel values, which we choose to be time-invariant but note that this strong constraint is not necessary in general.

The additional constraint beyond the OWL axioms is that some pixels are saturated, so that SAP is not possible. We consider instead the unsaturated pixels $p_j$ at the wings of the broad and structured PSF. We construct a light curve as a linear combination of these time series with weights $w_j$, so that flux at cadence $i$ is

@@

%  improvements
Unlike other methods for calibrating \kepler systematics, other than the value of $\delta$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm. The signal and the noise are jointly estimated from the data. The method is a self-calibration that is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise.

It is therefore likely that significant improvements can be made to the method by including cotrending basis vectors with mean zero and whose weights are allowed to be negative, which would represent systematics which are common to all pixels in the halo aperture and therefore masquerade as signal. Any linear combination of convex objective functions is itself convex, and future extensions to the method could enforce combinations of different lags and orders to better represent systematics occurring on different timescales (e.g. thruster firings, red noise) and with different levels of smoothness.
